Spatial Reasoning and Statistical Graphics

### 2014-10-16 Paper/Draft1/TestingVisualAptitude.Rnw
additional explanation of significance of calculus completion.

There is no significant difference in lineup performance for participants of different age, self-assessed skill rating, previous participation in math or science research, completion of a statistics class, or experience with AutoCAD.
% There is a significant difference between male and female performance on lineups; this is not particularly surprising, since men perform better on many spatial tests \citep{voyer1995magnitude} and performance on spatial tests is correlated with phase of the menstrual cycle in women \citep{hausmann2000sex}.
Completion of Calculus I is associated with increased performance on lineups. This may be related to general math education level, or it may be that success in both lineups and calculus requires certain visual skills. There is also a significant association between hours of video games played per week and score on lineups, however, this association is not monotonic and the groups do not have equal sample size, so the conclusion may be suspect.

>>>>

There is no significant difference in lineup performance for participants of different age, self-assessed skill rating, previous participation in math or science research, completion of a statistics class, or experience with AutoCAD.
% There is a significant difference between male and female performance on lineups; this is not particularly surprising, since men perform better on many spatial tests \citep{voyer1995magnitude} and performance on spatial tests is correlated with phase of the menstrual cycle in women \citep{hausmann2000sex}.
Completion of Calculus I is associated with increased performance on lineups. This may be related to general math education level, or it may be that success in both lineups and calculus requires certain visual skills. \newtext{This result is consistent with \citep{shah1995conceptual}, who found an association between  mathematical ability and performance on simple graph description tasks.}  There is also a significant association between hours of video games played per week and score on lineups, however, this association is not monotonic and the groups do not have equal sample size, so the conclusion may be suspect.
